On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-10-11 paper.tex
Written down star operation

\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
\[\xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
In addition, we require these maps to satisfy the following list of axioms:
\begin{enumerate}
 \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
 \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
 \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
 %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
 \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
\end{enumerate}

\end{dfn}
We want to define a relation on the set of triples $V = G_1 \times G_2 \times G_3$.
By definition, two triples $v = (x, y, z)$, $v'=(x', y', z')$ are said to be congruent (denoted $v \sim v'$)
 if there exists a triple $(a, b, c) \in G_{12}\times G_{13} \times G_{23}$ such that
\begin{align}
 x' =& x \cdot g_1^3(b) \cdot g_1^2(a), \\ 
 y' =& g_2^1(a)^{-1} \cdot y \cdot g_2^3(c), \\
 z' =& g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z.
\end{align}
\begin{lemma} 
 The relation $\sim$ is transitive. 
\end{lemma}
\begin{proof}
\begin{equation*} x'' = x' \cdot g_1^3(b') \cdot g_1^2(a') = 
 x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a') \end{equation*}
\begin{equation*} y'' = g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc') \end{equation*}

Using (3) for every $a \in G_{12}$, $b \in G_{13}$ one has $g_3^1(b^{g_1^2(a)}) = g_3^1(b)^{h_1 g_1^2(a)} = g_3^1(b)^{h_2g_2^1(a)}$.
Using (4) for every $c \in G_{23}$ and $z \in G_3$ one has $z ^{h_2 g_2^3(c)} = z^{ h_3 g_3^2(c)} = g_3^2(c)^{-1} \cdot z \cdot g_3^2(c)$;
Therefore:
\begin{multline*}
  z'' = g_2^3(c')^{-1} \cdot g_3^1(b')^{-h_2(y')} \cdot z' = g_2^3(c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \right)} g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z =
  \\ = g_2^3(cc')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \right)} \cdot g_3^1(b)^{-h_2(y)} \cdot z = 
       g_2^3(cc')^{-1} \cdot g_3^1(b \cdot b' ^ {g_1^2(a)^{-1}})^{- h_2 \left( y \right)} \cdot z.
\end{multline*}
\end{proof}

>>>>

\begin{dfn} {\it Tulenbaev's cube} is a collection of abstract groups and morphisms between them which make the diagram below commute.
\[\xymatrix{
G_{123} \ar[rr]_{f_{23}} \ar[dd]_{f_{12}} \ar[rd]_{f_{13}} &                        & G_{23} \ar[dd]^(.3){g_2^3} \ar[rd]^{g^2_3} &           \\
                                & G_{13} \ar[rr]^(.3){g^1_3} \ar^(.3){g^3_1}[dd] &                   & G_3 \ar[dd]_{h_3} \\
G_{12} \ar[rr]^(.3){g_2^1} \ar[rd]_{g_1^2}          &                        & G_2 \ar[rd]_{h_2}         &           \\
                                & G_1 \ar[rr]_{h_1}              &                   & G}\]
In addition, we require these maps to satisfy the following list of axioms:
\begin{enumerate}
 \item $G_1$ acts on $G_{13}$, $G$ acts on $G_3$ %??? vertical arrows $G_{13} \to G_1$ and $G_3 \to G$ are crossed modules
 \item for every $b \in G_{13}$ and $x \in G_1$ one has $g_1^3(b ^ x) = x^{-1} \cdot g_1^3(b) \cdot x$; (precrossed)
 \item for every $x\in G_{13}$, $b \in G_{13}$ one has $g_3^1(b^x) = g_3^1(b)^{h_1(x)}$; ($g_3^1$ map of precrossed modules?)
 %\item $g_3^1(b)^{h_1g_2^1(a)} = g_3^1(b^{g_1^2(a)})$
 \item for every $z_1, z_2 \in G_3$ one has $z_1^{-1} z_2 z_1 = z_2^{h_3(z_1)}$ (Peiffer)
\end{enumerate}
\end{dfn}
Now set $V = G_1 \times G_2 \times G_3$, $W = G_{12} \times G_{13} \times G_{23}$.
We define an operation $- \star - \colon W \times V \to V$ as follows. For $v = (x, y, z) \in V$ and $(a, b, c) \in W$ we set 
\[(a, b, c) \star (x, y, z) = (x \cdot g_1^3(b) \cdot g_1^2(a),\ g_2^1(a)^{-1} \cdot y \cdot g_2^3(c),\ g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z)\]

\begin{lemma} For every $v \in V$ one has 
 \begin{equation*}(a', b', c') \star \left( (a, b, c) \star v \right) = (a \cdot a', b \cdot {b'}^{g_1^2(a)^{-1}}, c \cdot c') \star v.\end{equation*}
\end{lemma}
\begin{proof}
Set $v'=(x', y', z') = (a, b, c) \star v$ and $(x'', y'', z'') = (a', b', c') \star v'$, then straightforward computation shows that:
\begin{align*} 
 x'' =& x' \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b) \cdot g_1^2(a) \cdot g_1^3(b') \cdot g_1^2(a') = x \cdot g_1^3(b \cdot b'^{g_1^2(a')^{-1}}) g_1^2(a \cdot a'),\\
 y'' =& g_2^1(a')^{-1} \cdot g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \cdot g_2^3(c') = g_2^1(aa')^{-1} \cdot y \cdot g_2^3(cc'). \end{align*}

Using (3) for every $a \in G_{12}$, $b \in G_{13}$ one has $g_3^1(b^{g_1^2(a)}) = g_3^1(b)^{h_1 g_1^2(a)} = g_3^1(b)^{h_2g_2^1(a)}$.
Using (4) for every $c \in G_{23}$ and $z \in G_3$ one has $z ^{h_2 g_2^3(c)} = z^{ h_3 g_3^2(c)} = g_3^2(c)^{-1} \cdot z \cdot g_3^2(c)$;
Therefore:
\begin{multline*}
  z'' = g_2^3(c')^{-1} \cdot g_3^1(b')^{-h_2(y')} \cdot z' = \\ 
  = g_2^3(c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \cdot g_2^3(c) \right)} g_3^2(c)^{-1} \cdot g_3^1(b)^{-h_2(y)} \cdot z = \\
  = g_2^3(c \cdot c')^{-1} \cdot g_3^1(b')^{- h_2 \left( g_2^1(a)^{-1} \cdot y \right)} \cdot g_3^1(b)^{-h_2(y)} \cdot z = \\
  = g_2^3(c \cdot c')^{-1} \cdot g_3^1(b \cdot {b'} ^ {g_1^2(a)^{-1}})^{- h_2 \left( y \right)} \cdot z. \qedhere
\end{multline*}
\end{proof}

Now we define a relation on the set $V$.
By definition, two elements $v$, $v'$ are declared congruent (denoted $v \sim v'$)
 if $v' = w \star v$ for some triple $(a, b, c) \in W$. In view of thea above lemma this relation is an equivalence relation
 and we denote the quotient set of $V$ modulo this relation by $V'$.
